### 2021-12-08 Paper/main.tex
Add files via upload

% THIS TEMPLATE IS A WORK IN PROGRESS

\documentclass{article}

\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{amsfonts,amsmath}
\usepackage{latexsym}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage{amsthm}

%\lhead{\includegraphics[width=0.2\textwidth]{nyush-logo.pdf}}
\fancypagestyle{firstpage}{%
  \lhead{NYU Shanghai}
  \rhead{
  %%%% COMMENT OUT / UNCOMMENT THE LINES BELOW TO FIT WITH YOUR MAJOR(S)
  %\&
  %Data
   Machine Learning 2021}
}

%%%% PROJECT TITLE
\title{Your Wonderful Project Topic}

%%%% NAMES OF ALL THE STUDENTS INVOLVED (first-name last-name)
\author{\href{mailto:author1@nyu.edu}{Author \#1}, \href{mailto:author2@nyu.edu}{Author \#2}}

\date{\vspace{-5ex}} %NO DATE

\begin{document}
\maketitle
\thispagestyle{firstpage}

\begin{abstract}
    A abstract sums up your work in very few sentences:
    (i) state the problem you are addressing;
    (ii) say why it’s an interesting problem, and which issues are hard to tackle; 
    (iii) give your approach towards solving the problem; 
    (iv) say Why and how well your approach solves the problem.
\end{abstract}

\section*{Introduction}

Your introduction briefly explains the problem you address, and what you’ve achieved towards solving the problem. It’s an edited and updated version of your introduction and objective from your topic proposal

\section*{Dataset}
Our project dataset is FIFA 2019 players attributes dataset, which is collected
from Kaggle. This dataset includes 89 attributes of a soccer player, and our
project only uses some of these attributes concerning only player capability.
Besides, considering that goalkeepers have a totally different set of capability
metrics compared with other players, we will only consider data records of nongoalkeepers in our model.\\
Now we beginning the data processing.
There are 18206 players for which 89 features each are provided. Fristly, we should drop the duplicate entries. 
Then we check the variables: 
\begin{center}
$ID, Name, Age, Photo, Nationality, Flag, Overall, Potential, Club, Club Logo, Value,$\\ 
$Wage, Special, Preferred Foot, International Reputation, Weak Foot, Skill Moves,$\\
$Work Rate, Body Type, Real Face, Position, Jersey Number, $\\
$Joined, Loaned From, Contract Valid Until,Height, Weight,$\\
$LS, ST, RS, LW, LF, CF, RF, RW, LAM, CAM, RAM, LM, LCM, CM,$\\
$RCM, RM, LWB, LDM, CDM, RDM, RWB, LB, LCB, CB, RCB, RB,$ \\
$Crossing, Finishing, HeadingAccuracy, ShortPassing, Volleys, Dribbling,$\\ 
$Curve, FKAccuracy, LongPassing, BallControl, Acceleration,$\\ 
$SprintSpeed, Agility, Reactions, Balance, ShotPower, Jumping, Stamina, Strength,$\\ $LongShots, Aggression, Interceptions, Positioning, Vision, Penalties, Composure,$\\ $Marking, StandingTackle, SlidingTackle,$\\
$GKDiving, GKHandling, GKKicking, GKPositioning,
GKReflexes, Release Clause$
\end{center}
\\
We have to delete the missing value which will distrubing our model. 
\begin{table}[]
\begin{tabular}{|l|l|l|l|}
\hline
\textit{Index} & \textit{column name}          & \textit{Total missing} & \textit{Percent missing} \\ \hline
\textit{0}     & \textit{Loaned From}          & \textit{16943}         & \textit{0.930576}        \\ \hline
\textit{1}     & \textit{LWB}                  & \textit{2085}          & \textit{0.114516}        \\ \hline
\textit{2}     & \textit{LM}                   & \textit{2085}          & \textit{0.114516}        \\ \hline
\textit{...}   & \textit{...}                  & \textit{...}           & \textit{...}             \\ \hline
\textit{23}    & \textit{RS}                   & \textit{2085}          & \textit{0.114516}        \\ \hline
\textit{24}    & \textit{ST}                   & \textit{2085}          & \textit{0.114516}        \\ \hline
\textit{25}    & \textit{LS}                   & \textit{2085}          & \textit{0.114516}        \\ \hline
\textit{26}    & \textit{RCB}                  & \textit{2085}          & \textit{0.114516}        \\ \hline
\textit{27}    & \textit{Release Clause}       & \textit{1564}          & \textit{0.085901}        \\ \hline
\textit{28}    & \textit{Joined}               & \textit{1553}          & \textit{0.085297}        \\ \hline
\textit{29}    & \textit{Contract Valid Until} & \textit{289}           & \textit{0.015873}        \\ \hline
..             & \textit{...}                  & \textit{...}           & \textit{...}             \\ \hline
\textit{58}    & \textit{Finishing}            & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{59}    & \textit{Crossing}             & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{60}    & \textit{Positioning}          & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{61}    & \textit{LongPassing}          & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{62}    & \textit{BallControl}          & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{63}    & \textit{Acceleration}         & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{64}    & \textit{SprintSpeed}          & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{65}    & \textit{FKAccuracy}           & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{66}    & \textit{Reactions}            & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{67}    & \textit{ShotPower}            & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{68}    & \textit{GKReflexes}           & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{69}    & \textit{Jumping}              & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{70}    & \textit{Stamina}              & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{71}    & \textit{Strength}             & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{72}    & \textit{LongShots}            & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{73}    & \textit{Aggression}           & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{74}    & \textit{Balance}              & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{75}    & \textit{Interceptions}        & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{76}    & \textit{Flag}                 & \textit{0}             & \textit{0.000000}        \\ \hline
\textit{77}    & \textit{Name}                 & \textit{0}             & \textit{0.000000}        \\ \hline
\textit{78}    & \textit{Age}                  & \textit{0}             & \textit{0.000000}        \\ \hline
\textit{79}    & \textit{Photo}                & \textit{0}             & \textit{0.000000}        \\ \hline
\textit{80}    & \textit{Nationality}          & \textit{0}             & \textit{0.000000}        \\ \hline
\textit{81}    & \textit{Value}                & \textit{0}             & \textit{0.000000}        \\ \hline
\textit{82}    & \textit{Overall}              & \textit{0}             & \textit{0.000000}        \\ \hline
\textit{83}    & \textit{Potential}            & \textit{0}             & \textit{0.000000}        \\ \hline
\textit{84}    & \textit{Club Logo}            & \textit{0}             & \textit{0.000000}        \\ \hline
\textit{85}    & \textit{Wage}                 & \textit{0}             & \textit{0.000000}        \\ \hline
\textit{86}    & \textit{Special}              & \textit{0}             & \textit{0.000000}        \\ \hline
\textit{87}    & \textit{ID}                   & \textit{0}             & \textit{0.000000}        \\ \hline
\end{tabular}
\end{table}

Conserning these missing value we have belowing comments:\\
(i) Since a big chunk of players are not loaned to other clubs, hence there are $16943$ missing values out of $18206$ i.e. they play for their own club.\\
(ii) There is a consistency $(11.45\%)$ in missing values for the position (they play on), this needs to be explored.\\
(iii) Release clause, joined, contract valid until, club, position, jersey number have missing values and need to be explored.\\
(iv) There is a consistency $(0.26\%)$ in missing values for the players rating attributes.

\section*{Solution}

The solution section covers all of your model design, algorithms, formulas, findings etc. It explains in detail each contribution, if possible with figures/schematics.

\section*{Results and Discussion}
The results section details your metrics and experiments for the assessment of your solution. It allows you to compare your idea with other approaches you've tested.

\nocite{*}
\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}

### 2021-12-08 Paper/main.tex
finish dataset process

@@
 \section*{Dataset}
+
+\subsection{Dateset overall}
+
 Our project dataset is FIFA 2019 players attributes dataset, which is collected
@@
 Besides, considering that goalkeepers have a totally different set of capability
-metrics compared with other players, we will only consider data records of nongoalkeepers in our model.\\
+metrics compared with other players, we will only consider data records of nongoalkeepers in our model.
+
+\subsection{Data processing}
+
 Now we beginning the data processing.
-There are 18206 players for which 89 features each are provided. Fristly, we should drop the duplicate entries. 
+There are 18206 players for which 89 features each are provided. Firstly, we should drop the duplicate entries. 
 Then we check the variables: 
@@
 \\
-We have to delete the missing value which will distrubing our model. 
+Now we have to delete the missing value which will distrubing our model.
+
 \begin{table}[]
+\centering
 \begin{tabular}{|l|l|l|l|}
@@
 \end{tabular}
+\caption{Missing value percent}
+\end{table}
+\newpage
+
+Considering these missing value we have below comments:
+\begin{itemize}
+    \item Since a big chunk of players are not loaned to other clubs, hence there are $16943$ missing values out of $18206$ i.e. they play for their own club.
+    \item There is a consistency $(11.45\%)$ in missing values for the position (they play on), this needs to be explored.
+    \item Release clause, joined, contract valid until, club, position, jersey number have missing values and need to be explored.
+    \item There is a consistency $(0.26\%)$ in missing values for the players rating attributes.
+\end{itemize}
+\\
+Now we will drop unnecessary columns, which can address the problem simply, reference the FIFA official guideline (https://www.fifauteam.com/fifa-19-attributes-guide/).
+we only keep significant values that have highly contributed to the model.
+
+\begin{center}
+$Age, Overall, Potential, Weak Foot, Position, Crossing, Finishing, HeadingAccuracy,$ \\
+$ShortPassing, Volleys, Dribbling, Curve, FKAccuracy, LongPassing, BallControl, Acceleration,$ \\
+$SprintSpeed, Agility, Reactions, Balance, ShotPower, Jumping, Stamina, Strength, LongShots,$\\
+$Aggression, Interceptions, Positioning, Vision, Penalties, Composure, Marking, StandingTackle,$ \\
+$SlidingTackle, GKDiving, GKHandling, GKKicking, GKPositioning, GKReflexes$
+\end{center}
+
+We have to delete the missing value which will disturbing our model and then we will filter data with null values for position:
+\\
+\clearpage
+\begin{table}[]
+\centering
+\begin{tabular}{|l|l|l|l|}
+\hline
+\textit{Index} & \textit{column name}   & \textit{Total missing} & \textit{Percent missing} \\ \hline
+\textit{0}     & \textit{Position}      & \textit{60}            & \textit{0.003295}        \\ \hline
+\textit{1}     & \textit{GKReflexes}    & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{2}     & \textit{Curve}         & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{...}   & \textit{...}           & \textit{...}           & \textit{...}             \\ \hline
+\textit{30}    & \textit{Positioning}   & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{31}    & \textit{Interceptions} & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{32}    & \textit{Aggression}    & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{33}    & \textit{LongShots}     & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{34}    & \textit{Strength}      & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{35}    & \textit{Stamina}       & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{36}    & \textit{Potential}     & \textit{0}             & \textit{0.000000}        \\ \hline
+\textit{37}    & \textit{Overall}       & \textit{0}             & \textit{0.000000}        \\ \hline
+\textit{38}    & \textit{Age}           & \textit{0}             & \textit{0.000000}        \\ \hline
+\end{tabular}
+\caption{Missing value percent in useful attribute}
 \end{table}
 
-Conserning these missing value we have belowing comments:\\
-(i) Since a big chunk of players are not loaned to other clubs, hence there are $16943$ missing values out of $18206$ i.e. they play for their own club.\\
-(ii) There is a consistency $(11.45\%)$ in missing values for the position (they play on), this needs to be explored.\\
-(iii) Release clause, joined, contract valid until, club, position, jersey number have missing values and need to be explored.\\
-(iv) There is a consistency $(0.26\%)$ in missing values for the players rating attributes.
+After handling these missing values we have 18147 rows thought, subtracting the 60 missing values.
+Besides, we have to transform some $string$ type values to $int$ type, which guarantees our model works.
+
+At last, we partition original player data according to positions, we mainly divide players into 4 positions: \textbf{Forward}, \textbf{Midfielder}, \textbf{Back}, and \textbf{Goalkeeper}.
 

### 2021-12-09 Paper/main.tex
Update data processing & regression code
- Updated data processing code to drop column "Potential". This is highly correlated to overall rating and is not an objective metric;
- Updated regression code. The data processing part in this code is removed since data has already been processed, and added some plotting code.
- Also added project topic, names and emails into the LaTex file.

@@
 %%%% PROJECT TITLE
-\title{Your Wonderful Project Topic}
+\title{Machine Learning Approach to Soccer Player's Overall Rating Prediction}
 
 %%%% NAMES OF ALL THE STUDENTS INVOLVED (first-name last-name)
-\author{\href{mailto:author1@nyu.edu}{Author \#1}, \href{mailto:author2@nyu.edu}{Author \#2}}
+\author{\href{mailto:ao2186@nyu.edu}{Antai Ouyang \#1}, \href{mailto:xl3215@nyu.edu}{Xianglong Li \#2}, \href{mailto:hl4151@nyu.edu}{Haochen Li \#3}}
 
@@
     (i) state the problem you are addressing;
-    (ii) say why it’s an interesting problem, and which issues are hard to tackle; 
+    (ii) say why it's an interesting problem, and which issues are hard to tackle; 
     (iii) give your approach towards solving the problem; 
@@
 
-Your introduction briefly explains the problem you address, and what you’ve achieved towards solving the problem.
-It’s an edited and updated version of your introduction and objective from your topic proposal
+Your introduction briefly explains the problem you address, and what you've achieved towards solving the problem.
+It's an edited and updated version of your introduction and objective from your topic proposal
 
@@
 \end{center}
-\\
-Now we have to delete the missing value which will distrubing our model.
+\par Now we have to delete the missing value which will distrubing our model.
 
@@
 \end{itemize}
-\\
-Now we will drop unnecessary columns, which can address the problem simply, reference the FIFA official guideline (https://www.fifauteam.com/fifa-19-attributes-guide/).
+\par Now we will drop unnecessary columns, which can address the problem simply, reference the FIFA official guideline (https://www.fifauteam.com/fifa-19-attributes-guide/).
 we only keep significant values that have highly contributed to the model.

### 2021-12-10 Paper/main.tex

--- 2021-12-08 Paper/main.tex
@@
 \begin{abstract}
-    A abstract sums up your work in very few sentences:
-    (i) state the problem you are addressing;
-    (ii) say why it’s an interesting problem, and which issues are hard to tackle; 
-    (iii) give your approach towards solving the problem; 
-    (iv) say Why and how well your approach solves the problem.
+
+    For this project, I am positioning myself as a scouting agency that uses analytics to, among other things, enhance the discovery of talents and help soccer clubs better understand the dynamics (features) that come into play when determining the value, overall and future potential of a player.
+
+    Although the $overall$ rating is the most important value either in the real football market or FIFA games, the official rating criteria is still not published. 
+    Our model is to predict the $overall$ rating of players given their several capability values, which use the data classified by players' position and the whole position data.
+    Besides, our
+    project only uses some of these attributes concerning only player capability according to official guideline.
+
+    To demonstrate the benefits of our model, we built various charts and evaluated it. In our experiments, neural networks could ... compared to liner regression.
+
 \end{abstract}
@@
 \section*{Introduction}
+The Fédération Internationale de Football Association (FIFA) will publish the
+overall rating and other metrics for soccer players every year. Although the
+metrics can affect the overall rating of a player, the exact rating criteria is still
+not published. Our project is to predict the overall rating of players given their
+capability values.
+Several data analyses projects have been designed for this dataset. However,
+these projects only focus on evaluating the metrics of players but failed to predict
+the overall rating of players. Some projects tried to predict the overall rating
+of players, but these projects still lack the comparison among different models
+to choose the best one or give any persuasive insights or conclusions. Our project tries different models for rating
+prediction and determine their performances to find the best model and give insightful conclusions and opinions.
 
-Your introduction briefly explains the problem you address, and what you’ve achieved towards solving the problem.
-It’s an edited and updated version of your introduction and objective from your topic proposal
+We implement regression methods in machine learning to this problem.
+We have trained our model based on a set of data randomly selected from our
+dataset, and then test our model on a stand-out test set also selected from our
+dataset. In this way, we create and validate a model predicting the overall
+rating of a player.
+
+Our project dataset is FIFA 2019 players attributes dataset, which is collected
+from Kaggle. This dataset includes 89 attributes of a soccer player, and our
+project only uses some of these attributes concerning only player capability.
+Besides, considering that goalkeepers have a totally different set of capability
+metrics compared with other players.
+
+We implement linear regression and neural networks in our project. For each model, we use cross validation to find the
+best hyperparameter for each model. We compare their performance based
+on their $r2 score$ and testing $RMSE$. Finally choose the most accurate model, neural networks. In order to finish this model fitting and predicting process, we plan
+to randomly select data from our dataset, and then split the selected data into
+training and testing sets to implement cross validation.
 

### 2021-12-10 Paper/main.tex
Dataset chapter updated
- Updated chapter Dataset in LaTeX file.

@@
 \usepackage{amsthm}
+\usepackage{makecell}
 
@@
 There are 18206 players for which 89 features each are provided. Firstly, we should drop the duplicate entries. 
-Then we check the variables: 
-\begin{center}
-$ID, Name, Age, Photo, Nationality, Flag, Overall, Potential, Club, Club Logo, Value,$\\ 
-$Wage, Special, Preferred Foot, International Reputation, Weak Foot, Skill Moves,$\\
-$Work Rate, Body Type, Real Face, Position, Jersey Number, $\\
-$Joined, Loaned From, Contract Valid Until,Height, Weight,$\\
-$LS, ST, RS, LW, LF, CF, RF, RW, LAM, CAM, RAM, LM, LCM, CM,$\\
-$RCM, RM, LWB, LDM, CDM, RDM, RWB, LB, LCB, CB, RCB, RB,$ \\
-$Crossing, Finishing, HeadingAccuracy, ShortPassing, Volleys, Dribbling,$\\ 
-$Curve, FKAccuracy, LongPassing, BallControl, Acceleration,$\\ 
-$SprintSpeed, Agility, Reactions, Balance, ShotPower, Jumping, Stamina, Strength,$\\ $LongShots, Aggression, Interceptions, Positioning, Vision, Penalties, Composure,$\\ $Marking, StandingTackle, SlidingTackle,$\\
-$GKDiving, GKHandling, GKKicking, GKPositioning,
-GKReflexes, Release Clause$
-\end{center}
-\\
-Now we have to delete the missing value which will distrubing our model.
+Then we check the columns (attributes). These columns can be grouped into 6 categories as follows:
 
@@
     \centering
-\begin{tabular}{|l|l|l|l|}
+    \begin{tabular}{|l|l|}
     \hline
-\textit{Index} & \textit{column name}          & \textit{Total missing} & \textit{Percent missing} \\ \hline
-\textit{0}     & \textit{Loaned From}          & \textit{16943}         & \textit{0.930576}        \\ \hline
-\textit{1}     & \textit{LWB}                  & \textit{2085}          & \textit{0.114516}        \\ \hline
-\textit{2}     & \textit{LM}                   & \textit{2085}          & \textit{0.114516}        \\ \hline
-\textit{...}   & \textit{...}                  & \textit{...}           & \textit{...}             \\ \hline
-\textit{23}    & \textit{RS}                   & \textit{2085}          & \textit{0.114516}        \\ \hline
-\textit{24}    & \textit{ST}                   & \textit{2085}          & \textit{0.114516}        \\ \hline
-\textit{25}    & \textit{LS}                   & \textit{2085}          & \textit{0.114516}        \\ \hline
-\textit{26}    & \textit{RCB}                  & \textit{2085}          & \textit{0.114516}        \\ \hline
-\textit{27}    & \textit{Release Clause}       & \textit{1564}          & \textit{0.085901}        \\ \hline
-\textit{28}    & \textit{Joined}               & \textit{1553}          & \textit{0.085297}        \\ \hline
-\textit{29}    & \textit{Contract Valid Until} & \textit{289}           & \textit{0.015873}        \\ \hline
-..             & \textit{...}                  & \textit{...}           & \textit{...}             \\ \hline
-\textit{58}    & \textit{Finishing}            & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{59}    & \textit{Crossing}             & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{60}    & \textit{Positioning}          & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{61}    & \textit{LongPassing}          & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{62}    & \textit{BallControl}          & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{63}    & \textit{Acceleration}         & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{64}    & \textit{SprintSpeed}          & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{65}    & \textit{FKAccuracy}           & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{66}    & \textit{Reactions}            & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{67}    & \textit{ShotPower}            & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{68}    & \textit{GKReflexes}           & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{69}    & \textit{Jumping}              & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{70}    & \textit{Stamina}              & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{71}    & \textit{Strength}             & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{72}    & \textit{LongShots}            & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{73}    & \textit{Aggression}           & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{74}    & \textit{Balance}              & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{75}    & \textit{Interceptions}        & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{76}    & \textit{Flag}                 & \textit{0}             & \textit{0.000000}        \\ \hline
-\textit{77}    & \textit{Name}                 & \textit{0}             & \textit{0.000000}        \\ \hline
-\textit{78}    & \textit{Age}                  & \textit{0}             & \textit{0.000000}        \\ \hline
-\textit{79}    & \textit{Photo}                & \textit{0}             & \textit{0.000000}        \\ \hline
-\textit{80}    & \textit{Nationality}          & \textit{0}             & \textit{0.000000}        \\ \hline
-\textit{81}    & \textit{Value}                & \textit{0}             & \textit{0.000000}        \\ \hline
-\textit{82}    & \textit{Overall}              & \textit{0}             & \textit{0.000000}        \\ \hline
-\textit{83}    & \textit{Potential}            & \textit{0}             & \textit{0.000000}        \\ \hline
-\textit{84}    & \textit{Club Logo}            & \textit{0}             & \textit{0.000000}        \\ \hline
-\textit{85}    & \textit{Wage}                 & \textit{0}             & \textit{0.000000}        \\ \hline
-\textit{86}    & \textit{Special}              & \textit{0}             & \textit{0.000000}        \\ \hline
-\textit{87}    & \textit{ID}                   & \textit{0}             & \textit{0.000000}        \\ \hline
+    \makecell[c]{\textit{Category}}     &       \makecell[c]{\textit{Attributes}} \\ \hline
+    \textit{Basic Information}          &       \makecell[c]{\textit{ID, Name, Age, Photo, Nationality, Real Face, Height, Weight,} \\
+                                                \textit{Body Type, Special, Flag, Position, Club, Club Logo, Work Rate,} \\
+                                                \textit{Jersey Number, Weak Foot, Preferred Foot, Skill Moves,} \\
+                                                \textit{International Reputation}} \\ \hline
+    \textit{Ratings}                    &       \makecell[c]{\textit{Overall, Potential, LS, ST, RS, LW, LF, CF, RF, RW, LAM,} \\
+                                                \textit{CAM, RAM, LM, LCM, CM, RCM, RM, LWB, LDM, CDM,} \\
+                                                \textit{RDM, RWB, LB, LCB, CB, RCB, RB}} \\ \hline
+    \textit{Market Value Related}       &       \makecell[c]{\textit{Value, Wage, Joined, Loaned From, Contract Valid Until,} \\
+                                                \textit{Release Clause}} \\ \hline
+    \textit{Abilities}                  &       \makecell[c]{\textit{Crossing, Finishing, HeadingAccuracy, ShortPassing, Volleys,} \\
+                                                \textit{Dribbling, Curve,FKAccuracy, LongPassing, BallControl,} \\
+                                                \textit{Acceleration, SprintSpeed, Agility, Reactions, Balance, ShotPower,} \\
+                                                \textit{Jumping, Stamina, Strength, LongShots, Aggression, Interceptions,} \\
+                                                \textit{Positioning, Vision, Penalties,Composure, Marking, StandingTackle,} \\ \textit{SlidingTackle}} \\ \hline
+    \textit{Goalkeeper Abilities}       &       \makecell[c]{\textit{GKDiving, GKHandling, GKKicking, GKPositioning, GKReflexes}} \\ \hline
     \end{tabular}
-\caption{Missing value percent}
+    \caption{Columns (attributes) in the original dataset.}
 \end{table}
-\newpage
 
-Considering these missing value we have below comments:
-\begin{itemize}
-    \item Since a big chunk of players are not loaned to other clubs, hence there are $16943$ missing values out of $18206$ i.e. they play for their own club.
-    \item There is a consistency $(11.45\%)$ in missing values for the position (they play on), this needs to be explored.
-    \item Release clause, joined, contract valid until, club, position, jersey number have missing values and need to be explored.
-    \item There is a consistency $(0.26\%)$ in missing values for the players rating attributes.
-\end{itemize}
-\\
-Now we will drop unnecessary columns, which can address the problem simply, reference the FIFA official guideline (https://www.fifauteam.com/fifa-19-attributes-guide/).
-we only keep significant values that have highly contributed to the model.
+\par Our model only focuses on predicting the overall rating of a player.
+Thus, we only need to keep those attributes related to the ability of players and drop the other irrelavent attributes.
+Besides, our model does not consider ratings on different positions for the same player.
+Thus, we only keep attributes as follows:
 
-\begin{center}
-$Age, Overall, Potential, Weak Foot, Position, Crossing, Finishing, HeadingAccuracy,$ \\
-$ShortPassing, Volleys, Dribbling, Curve, FKAccuracy, LongPassing, BallControl, Acceleration,$ \\
-$SprintSpeed, Agility, Reactions, Balance, ShotPower, Jumping, Stamina, Strength, LongShots,$\\
-$Aggression, Interceptions, Positioning, Vision, Penalties, Composure, Marking, StandingTackle,$ \\
-$SlidingTackle, GKDiving, GKHandling, GKKicking, GKPositioning, GKReflexes$
-\end{center}
+\begin{table}[]
+    \centering
+    \begin{tabular}{|l|l|}
+    \hline
+    \makecell[c]{\textit{Category}}     &       \makecell[c]{\textit{Attributes}} \\ \hline
+    \textit{Basic Information}          &       \makecell[c]{\textit{Age, Position}} \\ \hline
+    \textit{Ratings}                    &       \makecell[c]{\textit{Overall} (as target value)} \\ \hline
+    \textit{Abilities}                  &       \makecell[c]{\textit{Crossing, Finishing, HeadingAccuracy, ShortPassing, Volleys,} \\
+                                                \textit{Dribbling, Curve,FKAccuracy, LongPassing, BallControl,} \\
+                                                \textit{Acceleration, SprintSpeed, Agility, Reactions, Balance, ShotPower,} \\
+                                                \textit{Jumping, Stamina, Strength, LongShots, Aggression, Interceptions,} \\
+                                                \textit{Positioning, Vision, Penalties,Composure, Marking, StandingTackle,} \\ \textit{SlidingTackle}} \\ \hline
+    \textit{Goalkeeper Abilities}       &       \makecell[c]{\textit{GKDiving, GKHandling, GKKicking, GKPositioning, GKReflexes}} \\ \hline
+    \end{tabular}
+    \caption{Columns (attributes) in the dataset for model prediction.}
+\end{table}
 
-We have to delete the missing value which will disturbing our model and then we will filter data with null values for position:
-\\
-\clearpage
+\par After deleting all the irrelavent attributes, we still have to delete data records with missing values.
+These records are resulted from , and they could introduce errors into our prediction.
+The null values in each column are counted and sorted as follows:
+
 \begin{table}[]
@@
 \textit{2}     & \textit{Curve}                & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{3}     & \textit{Agility}              & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{4}     & \textit{SprintSpeed}          & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{5}     & \textit{Acceleration}         & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{6}     & \textit{BallControl}          & \textit{48}            & \textit{0.002636}        \\ \hline
 \textit{...}   & \textit{...}                  & \textit{...}           & \textit{...}             \\ \hline
-\textit{30}    & \textit{Positioning}   & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{31}    & \textit{Interceptions} & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{32}    & \textit{Aggression}    & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{33}    & \textit{LongShots}     & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{34}    & \textit{Strength}      & \textit{48}            & \textit{0.002636}        \\ \hline
 \textit{35}    & \textit{Stamina}              & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{36}    & \textit{Potential}     & \textit{0}             & \textit{0.000000}        \\ \hline
-\textit{37}    & \textit{Overall}       & \textit{0}             & \textit{0.000000}        \\ \hline
-\textit{38}    & \textit{Age}           & \textit{0}             & \textit{0.000000}        \\ \hline
+\textit{36}    & \textit{Overall}              & \textit{0}             & \textit{0.000000}        \\ \hline
+\textit{37}    & \textit{Age}                  & \textit{0}             & \textit{0.000000}        \\ \hline
 \end{tabular}
-\caption{Missing value percent in useful attribute}
+\caption{Missing value percent.}
 \end{table}
 
-After handling these missing values we have 18147 rows thought, subtracting the 60 missing values.
-Besides, we have to transform some $string$ type values to $int$ type, which guarantees our model works.
-
-At last, we partition original player data according to positions, we mainly divide players into 4 positions: \textbf{Forward}, \textbf{Midfielder}, \textbf{Back}, and \textbf{Goalkeeper}.
+\par After deleting these missing values, we have 18147 rows left.
+After that, we still should inspect the data types of each column, and we should ensure the input attributes of our model are all of type $int$ to guarantee that our model works.
+The only attribute violating this in our model prediction dataset is $Position$.
+This attribute only indicates the position of a soccer player.
+Thus, we can divide all records into different categories according to their positions.
+\par We mainly divide players into 4 positions: \textbf{Forward}, \textbf{Midfielder}, \textbf{Back}, and \textbf{Goalkeeper}, and 4 CSV files are built for each of these categories to store them separately.
+Specially, we also built a CSV file to store all data together after our processing above.
 

### 2021-12-11 Paper/main.tex
Update main.tex

@@
 
-    For this project, I am positioning myself as a scouting agency that uses analytics to, among other things, enhance the discovery of talents and help soccer clubs better understand the dynamics (features) that come into play when determining the value, overall and future potential of a player.
+    For this project, we are positioning ourselves as a scouting agency that uses analytics to, among other things, enhance the discovery of talents and help soccer clubs better understand the dynamics (features) that come into play when determining the overall ability of a player.
 
     Although the $overall$ rating is the most important value either in the real football market or FIFA games, the official rating criteria is still not published.
-    Our model is to predict the $overall$ rating of players given their several capability values, which use the data classified by players' position and the whole position data.
-    Besides, our
-    project only uses some of these attributes concerning only player capability according to official guideline.
+Our model is to predict the $overall$ rating of players given their several capability values.
+Specially, we will divide players' position into 4 categories: forwards / strikers, midfielders, backfielders and goalkeepers, and we will predict overall ratings for each of these categories respectively.
 
@@
 \section*{Introduction}
-The Fédération Internationale de Football Association (FIFA) will publish the
-overall rating and other metrics for soccer players every year. Although the
-metrics can affect the overall rating of a player, the exact rating criteria is still
-not published. Our project is to predict the overall rating of players given their
-capability values.
-Several data analyses projects have been designed for this dataset. However,
-these projects only focus on evaluating the metrics of players but failed to predict
-the overall rating of players. Some projects tried to predict the overall rating
-of players, but these projects still lack the comparison among different models
-to choose the best one or give any persuasive insights or conclusions. Our project tries different models for rating
-prediction and determine their performances to find the best model and give insightful conclusions and opinions.
+The Fédération Internationale de Football Association (FIFA) publishes the overall rating and other metrics for soccer players every year in its authorized soccer game.
+Intuitively, the metrics of a player can affect the overall rating of a player.
+However, the exact rating criteria is still not published.
+Data analysis on soccer players' performance and abilities are being more and more valued by current soccer clubs.
+Thus, our project aims to predict the overall rating of players given their capability values.
 
-We implement regression methods in machine learning to this problem.
-We have trained our model based on a set of data randomly selected from our
-dataset, and then test our model on a stand-out test set also selected from our
-dataset. In this way, we create and validate a model predicting the overall
-rating of a player.
+Several data analyses projects have been designed for this dataset. However, these projects only focus on evaluating the metrics of players but failed to predict
+the overall rating of players. Some projects tried to predict the overall rating of players, but these projects still lack the comparison among different models
+to choose the best one or give any persuasive insights or conclusions.
+Our project tries different models for rating prediction and determine their performances to find the best model and give insightful conclusions and opinions.
 
-Our project dataset is FIFA 2019 players attributes dataset, which is collected
-from Kaggle. This dataset includes 89 attributes of a soccer player, and our
-project only uses some of these attributes concerning only player capability.
-Besides, considering that goalkeepers have a totally different set of capability
-metrics compared with other players.
+We will implement regression methods in machine learning to this problem.
+We plan to train our model based on a set of training data randomly selected from our dataset, and then test our model on a stand-out test set also selected from our dataset.
+In this way, we can create and validate a model predicting the overall rating of a player.
 
-We implement linear regression and neural networks in our project. For each model, we use cross validation to find the
-best hyperparameter for each model. We compare their performance based
-on their $r2 score$ and testing $RMSE$. Finally choose the most accurate model, neural networks. In order to finish this model fitting and predicting process, we plan
-to randomly select data from our dataset, and then split the selected data into
-training and testing sets to implement cross validation.
+Our project dataset is FIFA 2019 players attributes dataset, which is collected from Kaggle.
+This dataset includes 89 attributes of a soccer player, and our project only uses some of these attributes concerning only player capability.
+Details of data processing will be deeply illustrated in Dataset chapter.
+
+We will implement linear regression and neural network in our project.
+Solution chapter gives the details of our models, including their hyperparameters.
+In order to finish this model fitting and predicting process, we plan to randomly select data from our dataset, and then split the selected data into training and testing sets to implement cross validation.
+
+We will evaluate and compare the performance of these 2 models based on their $r2 score$ and testing $RMSE$.
+Besides, we will inspect the difference between these 2 models in practical use, and will mainly evaluate the usefulness of parameters of linear regression.
+This part will be further discussed in Results and Discussion chapter.
 
@@
 
-\begin{table}[]
+\begin{table}[htpb]
     \centering
@@
                                                 \textit{Body Type, Special, Flag, Position, Club, Club Logo, Work Rate,} \\
-                                                \textit{Jersey Number, Weak Foot, Preferred Foot, Skill Moves,} \\
-                                                \textit{International Reputation}} \\ \hline
+                                                \textit{Jersey Number, Weak Foot, Preferred Foot, Skill Moves, Reputation}} \\ \hline
     \textit{Ratings}                    &       \makecell[c]{\textit{Overall, Potential, LS, ST, RS, LW, LF, CF, RF, RW, LAM,} \\
@@
                                                 \textit{RDM, RWB, LB, LCB, CB, RCB, RB}} \\ \hline
-    \textit{Market Value Related}       &       \makecell[c]{\textit{Value, Wage, Joined, Loaned From, Contract Valid Until,} \\
-                                                \textit{Release Clause}} \\ \hline
-    \textit{Abilities}                  &       \makecell[c]{\textit{Crossing, Finishing, HeadingAccuracy, ShortPassing, Volleys,} \\
-                                                \textit{Dribbling, Curve,FKAccuracy, LongPassing, BallControl,} \\
-                                                \textit{Acceleration, SprintSpeed, Agility, Reactions, Balance, ShotPower,} \\
-                                                \textit{Jumping, Stamina, Strength, LongShots, Aggression, Interceptions,} \\
-                                                \textit{Positioning, Vision, Penalties,Composure, Marking, StandingTackle,} \\ \textit{SlidingTackle}} \\ \hline
+    \textit{Market Value Related}       &       \makecell[c]{\textit{Value, Wage, Joined, Loaned From, Contract Valid Until, Release Clause}} \\ \hline
+    \textit{Abilities}                  &       \makecell[c]{\textit{Crossing, Finishing, HeadingAccuracy, ShortPassing, Volleys, Dribbling,} \\
+                                                \textit{Curve,FKAccuracy, LongPassing, BallControl, Acceleration, SprintSpeed,} \\
+                                                \textit{Agility, Reactions, Balance, ShotPower, Jumping, Stamina, Strength,} \\
+                                                \textit{LongShots, Aggression, Interceptions, Positioning, Vision, Penalties,} \\
+                                                \textit{Composure, Marking, StandingTackle, SlidingTackle}} \\ \hline
     \textit{Goalkeeper Abilities}       &       \makecell[c]{\textit{GKDiving, GKHandling, GKKicking, GKPositioning, GKReflexes}} \\ \hline
@@
     \textit{Ratings}                    &       \makecell[c]{\textit{Overall} (as target value)} \\ \hline
-    \textit{Abilities}                  &       \makecell[c]{\textit{Crossing, Finishing, HeadingAccuracy, ShortPassing, Volleys,} \\
-                                                \textit{Dribbling, Curve,FKAccuracy, LongPassing, BallControl,} \\
-                                                \textit{Acceleration, SprintSpeed, Agility, Reactions, Balance, ShotPower,} \\
-                                                \textit{Jumping, Stamina, Strength, LongShots, Aggression, Interceptions,} \\
-                                                \textit{Positioning, Vision, Penalties,Composure, Marking, StandingTackle,} \\ \textit{SlidingTackle}} \\ \hline
+    \textit{Abilities}                  &       \makecell[c]{\textit{Crossing, Finishing, HeadingAccuracy, ShortPassing, Volleys, Dribbling,} \\
+                                                \textit{Curve,FKAccuracy, LongPassing, BallControl, Acceleration, SprintSpeed,} \\
+                                                \textit{Agility, Reactions, Balance, ShotPower, Jumping, Stamina, Strength,} \\
+                                                \textit{LongShots, Aggression, Interceptions, Positioning, Vision, Penalties,} \\
+                                                \textit{Composure, Marking, StandingTackle, SlidingTackle}} \\ \hline
     \textit{Goalkeeper Abilities}       &       \makecell[c]{\textit{GKDiving, GKHandling, GKKicking, GKPositioning, GKReflexes}} \\ \hline
@@
 \par After deleting all the irrelavent attributes, we still have to delete data records with missing values.
-These records are resulted from , and they could introduce errors into our prediction.
+These records are resulted from the lack of player information of some small clubs, and they could introduce errors into our prediction.
 The null values in each column are counted and sorted as follows:
@@
 \textit{3}     & \textit{Agility}              & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{4}     & \textit{SprintSpeed}          & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{5}     & \textit{Acceleration}         & \textit{48}            & \textit{0.002636}        \\ \hline
-\textit{6}     & \textit{BallControl}          & \textit{48}            & \textit{0.002636}        \\ \hline
 \textit{...}   & \textit{...}                  & \textit{...}           & \textit{...}             \\ \hline
@@
 
-\par After deleting these missing values, we have 18147 rows left.
-After that, we still should inspect the data types of each column, and we should ensure the input attributes of our model are all of type $int$ to guarantee that our model works.
+\par By observing these missing values in our dataset, all missing data lies in the 60 records with missing $Position$ value.
+After deleting these records with missing values, we have 18147 rows left in our dataset.
+After that, we still should inspect the data types of each column, and this is to ensure the input attributes of our model are all of type $int$ to guarantee that our model works.
 The only attribute violating this in our model prediction dataset is $Position$.
 This attribute only indicates the position of a soccer player.
-Thus, we can divide all records into different categories according to their positions.
-\par We mainly divide players into 4 positions: \textbf{Forward}, \textbf{Midfielder}, \textbf{Back}, and \textbf{Goalkeeper}, and 4 CSV files are built for each of these categories to store them separately.
-Specially, we also built a CSV file to store all data together after our processing above.
+\par We divide all records into different categories according to their positions.
+In this way, we can get rid of this String-typed attribute.
+Besides, in real soccer industry, players can actually be categoried according to their positions.
+We mainly divide players into 4 positions: \textbf{Forward}, \textbf{Midfielder}, \textbf{Back}, and \textbf{Goalkeeper}.
+Besides, for prediction on players on any position, we also keep the original dataset, but only delete its $Position$ column.
+\par Finally, we implement data normalization on each column. We use the expression below to calculate normalized data:
+$$Normalized = \frac{Original-Mean}{Variance}$$
+In which $Mean$ and $Variance$ are the mean and variance of the original data $Original$.
+After this normalization, we output all 4 categoried datasets and the original dataset into 5 CSV files respectively.
 
 \section*{Solution}
+\subsection*{Feature Engineering}
+The process of taking raw data and extracting or creating new features that allow a machine learning model to learn a mapping between these features and the target.
+This might mean taking transformations of variables, such as we did with the log and square root, or one-hot encoding categorical variables so they can be used in a model.
+Generally, we think of feature engineering as adding additional features derived from the raw data.
+In this project, we take the following steps:
+\begin{itemize}
+    \item Group similar data(delete positions rating)
+    \item Convert object type variables to numerical by label encoding(transform string type to int type)
+\end{itemize}
 
-The solution section covers all of your model design, algorithms, formulas, findings etc. It explains in detail each contribution, if possible with figures/schematics.
+\subsection*{Feature Selection}
+ The process of choosing the most relevant features in your data.
+"Most relevant" can depend on many factors, but it might be something as simple as the highest correlation with the target, or the features with the most variance.
+In feature selection, we remove features that do not help our model learn the relationship between features and the target.
+This can help the model generalize better to new data and results in a more interpretable model.
+Generally, I think of feature selection as subtracting features so we are left with only those that are most important.
+In this project, we take the following steps:
+\begin{itemize}
+    \item Delete missing values
+    \item Remove features features that do not have a significant effect on the dependent variable or prediction of output by backward elimination.
+\end{itemize}
 

### 2021-12-11 Paper/main.tex
Update main.tex

@@
 
-\subsection{Dateset overall}
+\subsection*{Dateset overall}
 
@@
 
-\subsection{Data processing}
+\subsection*{Data processing}
 
@@
 \section*{Solution}
+We implement 5 models \textbf{Linear Regression}, \textbf{Random Forest}, \textbf{Gradient Boosted}, \textbf{K-Nearest Neighbors} and \textbf{Neural Network}. Below, we will introduce our workflow.
+
 \subsection*{Feature Engineering}
@@
 
+\subsection*{Model}.
+We will compare five different machine learning models using the great Scikit-Learn library:
+\begin{itemize}
+    \item Linear Regression
+    \item Random Forest Regression
+    \item Gradient Boosting Regression
+    \item K-Nearest Neighbors Regression
+    \item Neutral Network
+\end{itemize}
+
+To compare the models, we are going to be mostly using the Scikit-Learn defaults for the model hyperparameters.
+Generally these will perform decently, but should be optimized before actually using a model.
+At first, we just want to determine the baseline performance of each model, and then we can select the best performing model for further optimization using hyperparameter tuning.
+The default hyperparameters will get a model up and running, but nearly always should be adjusted using some sort of search to find the best settings for your problem!
+
+\subsection*{Metric:}
+\subsubsection*{Root Mean Square Error}
+Root Mean Square Error (RMSE) is the standard deviation of the residuals (prediction errors).
+Residuals are a measure of how far from the regression line data points are; RMSE is a measure of how spread out these residuals are.
+In other words, it tells you how concentrated the data is around the line of best fit.
+Root mean square error is commonly used in climatology, forecasting, and regression analysis to verify experimental results.
+
+\subsubsection*{$R^2$ Score}
+The $R^2score$ function computes the coefficient of determination.
+It represents the proportion of variance (of y) that has been explained by the independent variables in the model.
+It provides an indication of goodness of fit and therefore a measure of how well unseen samples are likely to be predicted by the model, through the proportion of explained variance.
+
+\begin{center}
+\includegraphics[scale=0.5]{rmse.png}\\
+\caption{Image 1, Model Comparison on RMSE}\\
+\includegraphics[scale=0.5]{r2score.png} \\
+\caption{Image 2, Model Comparison on $R^2$ Score}
+\end{center}
+
+Depending on the run (the exact results change slighty each time), the Neutral Network performs the best.
+We have to admit that this is not the most fair comparison because we are using mostly the default hyperparameters.
+Nonetheless, from these results, we can conclude that machine learning is applicable because all the models significantly outperform the baseline!
+From here, We are going to concentrate on optimizing the best model using hyperparamter tuning. Given the results here, we will concentrate on using the Linear Regression and  Neutral Network.
+
+\subsection*{Model Optimization}
+In machine learning, optimizing a model means finding the best set of hyperparameters for a particular problem.
+
+\subsubsection*{Hyperparameters}
+First of all, we need to understand what model hyperparameters are in contrast to model parameters :
+
+Model hyperparameters are best thought of as settings for a machine learning algorithm that are tuned by the data scientist before training.
+Examples would be the number of trees in the random forest, or the number of neighbors used in K Nearest Neighbors Regression.
+Model parameters are what the model learns during training, such as the weights in the linear regression.
+We as data scientists control a model by choosing the hyperparameters, and these choices can have a significant effect on the final performance of the model (although usually not as great of an effect as getting more data or engineering features).
+Tuning the model hyperparameters controls the balance of under vs over fitting in a model.
+We can try to correct for under-fitting by making a more complex model, such as using more trees in a random forest or more layers in a deep neural network.
+A model that underfits has high bias, and occurs when our model does not have enough capacity (degrees of freedom) to learn the relationship between the features and the target.
+We can try to correct for overfitting by limiting the complexity of the model and applying regularization.
+This might mean decreasing the degree of a polynomial regression, or adding dropout layers to a deep neural network.
+A model that overfits has high variance and in effect has memorized the training set.
+Both underfitting and overfitting lead to poor generalization performance on the test set.
+The problem with choosing the hyperparameters is that no set will work best across all problems.
+Therefore, for every new dataset, we have to find the best settings.
+This can be a time-consuming process, but luckily there are several options for performing this procedure in Scikit-Learn.
+
+\subsection*{Evaluate Final Model on the Test Set}
+
 \section*{Results and Discussion}

### 2021-12-11 Paper/main.tex

@@
 % THIS TEMPLATE IS A WORK IN PROGRESS
+
+\documentclass{article}
+
+\usepackage{hyperref}
+\usepackage{fancyhdr}
+\usepackage{amsfonts,amsmath}
+\usepackage{latexsym}
+\usepackage{fullpage}
+\usepackage{graphicx}
+\usepackage{tikz}
+\usepackage{enumitem}
+\usepackage{amsthm}
+
+%\lhead{\includegraphics[width=0.2\textwidth]{nyush-logo.pdf}}
+\fancypagestyle{firstpage}{%
+  \lhead{NYU Shanghai}
+  \rhead{
+  %%%% COMMENT OUT / UNCOMMENT THE LINES BELOW TO FIT WITH YOUR MAJOR(S)
+  %\&
+  %Data
+   Machine Learning 2021}
+}
+
+%%%% PROJECT TITLE
+\title{Your Wonderful Project Topic}
+
+%%%% NAMES OF ALL THE STUDENTS INVOLVED (first-name last-name)
+\author{\href{mailto:author1@nyu.edu}{Author \#1}, \href{mailto:author2@nyu.edu}{Author \#2}}
+
+\date{\vspace{-5ex}} %NO DATE
+
+\begin{document}
+\maketitle
+\thispagestyle{firstpage}
+
+\begin{abstract}
+
+    For this project, I am positioning myself as a scouting agency that uses analytics to, among other things, enhance the discovery of talents and help soccer clubs better understand the dynamics (features) that come into play when determining the value, overall and future potential of a player.
+
+    Although the $overall$ rating is the most important value either in the real football market or FIFA games, the official rating criteria is still not published. 
+    Our model is to predict the $overall$ rating of players given their several capability values, which use the data classified by players' position and the whole position data.
+    Besides, our
+    project only uses some of these attributes concerning only player capability according to official guideline.
+
+    To demonstrate the benefits of our model, we built various charts and evaluated it. In our experiments, neural networks could ... compared to liner regression.
+
+\end{abstract}
+
+\section*{Introduction}
+The Fédération Internationale de Football Association (FIFA) will publish the
+overall rating and other metrics for soccer players every year. Although the
+metrics can affect the overall rating of a player, the exact rating criteria is still
+not published. Our project is to predict the overall rating of players given their
+capability values.
+Several data analyses projects have been designed for this dataset. However,
+these projects only focus on evaluating the metrics of players but failed to predict
+the overall rating of players. Some projects tried to predict the overall rating
+of players, but these projects still lack the comparison among different models
+to choose the best one or give any persuasive insights or conclusions. Our project tries different models for rating
+prediction and determine their performances to find the best model and give insightful conclusions and opinions.
+
+We implement regression methods in machine learning to this problem.
+We have trained our model based on a set of data randomly selected from our
+dataset, and then test our model on a stand-out test set also selected from our
+dataset. In this way, we create and validate a model predicting the overall
+rating of a player.
+
+Our project dataset is FIFA 2019 players attributes dataset, which is collected
+from Kaggle. This dataset includes 89 attributes of a soccer player, and our
+project only uses some of these attributes concerning only player capability.
+Besides, considering that goalkeepers have a totally different set of capability
+metrics compared with other players.
+
+We implement linear regression and neural networks in our project. For each model, we use cross validation to find the
+best hyperparameter for each model. We compare their performance based
+on their $r2 score$ and testing $RMSE$. Finally choose the most accurate model, neural networks. In order to finish this model fitting and predicting process, we plan
+to randomly select data from our dataset, and then split the selected data into
+training and testing sets to implement cross validation.
+
+\section*{Dataset}
+
+\subsection{Dateset overall}
+
+Our project dataset is FIFA 2019 players attributes dataset, which is collected
+from Kaggle. This dataset includes 89 attributes of a soccer player, and our
+project only uses some of these attributes concerning only player capability.
+Besides, considering that goalkeepers have a totally different set of capability
+metrics compared with other players, we will only consider data records of nongoalkeepers in our model.
+
+\subsection{Data processing}
+
+Now we beginning the data processing.
+There are 18206 players for which 89 features each are provided. Firstly, we should drop the duplicate entries. 
+Then we check the variables: 
+\begin{center}
+$ID, Name, Age, Photo, Nationality, Flag, Overall, Potential, Club, Club Logo, Value,$\\ 
+$Wage, Special, Preferred Foot, International Reputation, Weak Foot, Skill Moves,$\\
+$Work Rate, Body Type, Real Face, Position, Jersey Number, $\\
+$Joined, Loaned From, Contract Valid Until,Height, Weight,$\\
+$LS, ST, RS, LW, LF, CF, RF, RW, LAM, CAM, RAM, LM, LCM, CM,$\\
+$RCM, RM, LWB, LDM, CDM, RDM, RWB, LB, LCB, CB, RCB, RB,$ \\
+$Crossing, Finishing, HeadingAccuracy, ShortPassing, Volleys, Dribbling,$\\ 
+$Curve, FKAccuracy, LongPassing, BallControl, Acceleration,$\\ 
+$SprintSpeed, Agility, Reactions, Balance, ShotPower, Jumping, Stamina, Strength,$\\ $LongShots, Aggression, Interceptions, Positioning, Vision, Penalties, Composure,$\\ $Marking, StandingTackle, SlidingTackle,$\\
+$GKDiving, GKHandling, GKKicking, GKPositioning,
+GKReflexes, Release Clause$
+\end{center}
+\\
+Now we have to delete the missing value which will distrubing our model.
+
+\begin{table}[]
+\centering
+\begin{tabular}{|l|l|l|l|}
+\hline
+\textit{Index} & \textit{column name}          & \textit{Total missing} & \textit{Percent missing} \\ \hline
+\textit{0}     & \textit{Loaned From}          & \textit{16943}         & \textit{0.930576}        \\ \hline
+\textit{1}     & \textit{LWB}                  & \textit{2085}          & \textit{0.114516}        \\ \hline
+\textit{2}     & \textit{LM}                   & \textit{2085}          & \textit{0.114516}        \\ \hline
+\textit{...}   & \textit{...}                  & \textit{...}           & \textit{...}             \\ \hline
+\textit{23}    & \textit{RS}                   & \textit{2085}          & \textit{0.114516}        \\ \hline
+\textit{24}    & \textit{ST}                   & \textit{2085}          & \textit{0.114516}        \\ \hline
+\textit{25}    & \textit{LS}                   & \textit{2085}          & \textit{0.114516}        \\ \hline
+\textit{26}    & \textit{RCB}                  & \textit{2085}          & \textit{0.114516}        \\ \hline
+\textit{27}    & \textit{Release Clause}       & \textit{1564}          & \textit{0.085901}        \\ \hline
+\textit{28}    & \textit{Joined}               & \textit{1553}          & \textit{0.085297}        \\ \hline
+\textit{29}    & \textit{Contract Valid Until} & \textit{289}           & \textit{0.015873}        \\ \hline
+..             & \textit{...}                  & \textit{...}           & \textit{...}             \\ \hline
+\textit{58}    & \textit{Finishing}            & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{59}    & \textit{Crossing}             & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{60}    & \textit{Positioning}          & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{61}    & \textit{LongPassing}          & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{62}    & \textit{BallControl}          & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{63}    & \textit{Acceleration}         & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{64}    & \textit{SprintSpeed}          & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{65}    & \textit{FKAccuracy}           & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{66}    & \textit{Reactions}            & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{67}    & \textit{ShotPower}            & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{68}    & \textit{GKReflexes}           & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{69}    & \textit{Jumping}              & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{70}    & \textit{Stamina}              & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{71}    & \textit{Strength}             & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{72}    & \textit{LongShots}            & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{73}    & \textit{Aggression}           & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{74}    & \textit{Balance}              & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{75}    & \textit{Interceptions}        & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{76}    & \textit{Flag}                 & \textit{0}             & \textit{0.000000}        \\ \hline
+\textit{77}    & \textit{Name}                 & \textit{0}             & \textit{0.000000}        \\ \hline
+\textit{78}    & \textit{Age}                  & \textit{0}             & \textit{0.000000}        \\ \hline
+\textit{79}    & \textit{Photo}                & \textit{0}             & \textit{0.000000}        \\ \hline
+\textit{80}    & \textit{Nationality}          & \textit{0}             & \textit{0.000000}        \\ \hline
+\textit{81}    & \textit{Value}                & \textit{0}             & \textit{0.000000}        \\ \hline
+\textit{82}    & \textit{Overall}              & \textit{0}             & \textit{0.000000}        \\ \hline
+\textit{83}    & \textit{Potential}            & \textit{0}             & \textit{0.000000}        \\ \hline
+\textit{84}    & \textit{Club Logo}            & \textit{0}             & \textit{0.000000}        \\ \hline
+\textit{85}    & \textit{Wage}                 & \textit{0}             & \textit{0.000000}        \\ \hline
+\textit{86}    & \textit{Special}              & \textit{0}             & \textit{0.000000}        \\ \hline
+\textit{87}    & \textit{ID}                   & \textit{0}             & \textit{0.000000}        \\ \hline
+\end{tabular}
+\caption{Missing value percent}
+\end{table}
+\newpage
+
+Considering these missing value we have below comments:
+\begin{itemize}
+    \item Since a big chunk of players are not loaned to other clubs, hence there are $16943$ missing values out of $18206$ i.e. they play for their own club.
+    \item There is a consistency $(11.45\%)$ in missing values f% THIS TEMPLATE IS A WORK IN PROGRESS
 
@@
 \end{document}
+or the position (they play on), this needs to be explored.
+    \item Release clause, joined, contract valid until, club, position, jersey number have missing values and need to be explored.
+    \item There is a consistency $(0.26\%)$ in missing values for the players rating attributes.
+\end{itemize}
+\\
+Now we will drop unnecessary columns, which can address the problem simply, reference the FIFA official guideline (https://www.fifauteam.com/fifa-19-attributes-guide/).
+we only keep significant values that have highly contributed to the model.
+
+\begin{center}
+$Age, Overall, Potential, Weak Foot, Position, Crossing, Finishing, HeadingAccuracy,$ \\
+$ShortPassing, Volleys, Dribbling, Curve, FKAccuracy, LongPassing, BallControl, Acceleration,$ \\
+$SprintSpeed, Agility, Reactions, Balance, ShotPower, Jumping, Stamina, Strength, LongShots,$\\
+$Aggression, Interceptions, Positioning, Vision, Penalties, Composure, Marking, StandingTackle,$ \\
+$SlidingTackle, GKDiving, GKHandling, GKKicking, GKPositioning, GKReflexes$
+\end{center}
+
+We have to delete the missing value which will disturbing our model and then we will filter data with null values for position:
+\\
+\clearpage
+\begin{table}[]
+\centering
+\begin{tabular}{|l|l|l|l|}
+\hline
+\textit{Index} & \textit{column name}   & \textit{Total missing} & \textit{Percent missing} \\ \hline
+\textit{0}     & \textit{Position}      & \textit{60}            & \textit{0.003295}        \\ \hline
+\textit{1}     & \textit{GKReflexes}    & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{2}     & \textit{Curve}         & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{...}   & \textit{...}           & \textit{...}           & \textit{...}             \\ \hline
+\textit{30}    & \textit{Positioning}   & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{31}    & \textit{Interceptions} & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{32}    & \textit{Aggression}    & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{33}    & \textit{LongShots}     & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{34}    & \textit{Strength}      & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{35}    & \textit{Stamina}       & \textit{48}            & \textit{0.002636}        \\ \hline
+\textit{36}    & \textit{Potential}     & \textit{0}             & \textit{0.000000}        \\ \hline
+\textit{37}    & \textit{Overall}       & \textit{0}             & \textit{0.000000}        \\ \hline
+\textit{38}    & \textit{Age}           & \textit{0}             & \textit{0.000000}        \\ \hline
+\end{tabular}
+\caption{Missing value percent in useful attribute}
+\end{table}
+
+After handling these missing values we have 18147 rows thought, subtracting the 60 missing values.
+Besides, we have to transform some $string$ type values to $int$ type, which guarantees our model works.
+
+At last, we partition original player data according to positions, we mainly divide players into 4 positions: \textbf{Forward}, \textbf{Midfielder}, \textbf{Back}, and \textbf{Goalkeeper}.
+
+\section*{Solution}
+
+The solution section covers all of your model design, algorithms, formulas, findings etc. It explains in detail each contribution, if possible with figures/schematics.
+
+\section*{Results and Discussion}
+The results section details your metrics and experiments for the assessment of your solution. It allows you to compare your idea with other approaches you've tested.
+
+\nocite{*}
+\bibliographystyle{IEEEtran}
+\bibliography{references}
+
+\end{document}

### 2021-12-11 Paper/main.tex
testset

--- 2021-12-11 Paper/main.tex
@@
 \subsection*{Evaluate Final Model on the Test Set}
+We will use the best model from hyperparameter tuning to make predictions on the testing set.
+Our model has never seen the test set before, so this performance should be a good indicator of how the model would perform if deployed in the real world.
+
+\begin{center}
+\includegraphics[scale=0.5]{liner.png}\\
+\caption{Image 3, Linear Model for Overall Rating Prediction}\\
+\includegraphics[scale=0.5]{nn.png} \\
+\caption{Image 4, Neutral Network Model for Overall Rating Prediction}
+\end{center}
 

### 2021-12-11 Paper/main.tex
Updated main.tex

--- 2021-12-11 Paper/main.tex
@@
 \usepackage{makecell}
+\usepackage{graphicx}
 
@@
 Besides, our model does not consider ratings on different positions for the same player.
-Thus, we only keep attributes as follows:
-
-\begin{table}[htpb]
-    \centering
-    \begin{tabular}{|l|l|}
-    \hline
-    \makecell[c]{\textit{Category}}     &       \makecell[c]{\textit{Attributes}} \\ \hline
-    \textit{Basic Information}          &       \makecell[c]{\textit{Age, Position}} \\ \hline
-    \textit{Ratings}                    &       \makecell[c]{\textit{Overall} (as target value)} \\ \hline
-    \textit{Abilities}                  &       \makecell[c]{\textit{Crossing, Finishing, HeadingAccuracy, ShortPassing, Volleys, Dribbling,} \\
-                                                \textit{Curve,FKAccuracy, LongPassing, BallControl, Acceleration, SprintSpeed,} \\
-                                                \textit{Agility, Reactions, Balance, ShotPower, Jumping, Stamina, Strength,} \\
-                                                \textit{LongShots, Aggression, Interceptions, Positioning, Vision, Penalties,} \\
-                                                \textit{Composure, Marking, StandingTackle, SlidingTackle}} \\ \hline
-    \textit{Goalkeeper Abilities}       &       \makecell[c]{\textit{GKDiving, GKHandling, GKKicking, GKPositioning, GKReflexes}} \\ \hline
-    \end{tabular}
-    \caption{Columns (attributes) in the dataset for model prediction.}
-\end{table}
+Thus, we only keep all $Abilities$, all $Goalkeeper\; Abilities$, $Age$ and $Position$ in $Basic\; Information$, and $Overall$ in ratings as our target value.
 
@@
 
-\begin{center}
-\includegraphics[scale=0.5]{rmse.png}\\
-\caption{Image 1, Model Comparison on RMSE}\\
-\includegraphics[scale=0.5]{r2score.png} \\
-\caption{Image 2, Model Comparison on $R^2$ Score}
-\end{center}
+\begin{figure}[!htb]
+	\centering
+    \includegraphics[scale=0.35]{rmse.png}
+    \caption{Model Comparison on RMSE}\label{fig1}
+\end{figure}
 
+\begin{figure}[!htb]
+	\centering
+    \includegraphics[scale=0.35]{r2score.png}
+    \caption{Model Comparison on $R^2$ Score}\label{fig2}
+\end{figure}
+
+Figures \ref{fig1} and \ref{fig2} shows our results of running all 5 models mentioned above.
 Depending on the run (the exact results change slighty each time), the Neutral Network performs the best.
 We have to admit that this is not the most fair comparison because we are using mostly the default hyperparameters.
-Nonetheless, from these results, we can conclude that machine learning is applicable because all the models significantly outperform the baseline!
-From here, We are going to concentrate on optimizing the best model using hyperparamter tuning. Given the results here, we will concentrate on using the Linear Regression and  Neutral Network.
+Nonetheless, from these results, we can conclude that machine learning is applicable because all the models significantly outperform the baseline.
+From here, We are going to concentrate on optimizing the best model using hyperparamter tuning.
+Given the results here, Neutral Network has the best performance of all these 5 models.
+However, consider that only linear regression can give coefficients for each attributes among all these models, linear regression can generate more information and has higher usability than other models.
+Thus, we will focus on both linear regression and neural network in the following part.
 
@@
 Examples would be the number of trees in the random forest, or the number of neighbors used in K Nearest Neighbors Regression.
+
 Model parameters are what the model learns during training, such as the weights in the linear regression.
@@
 
-\subsection*{Evaluate Final Model on the Test Set}
+\section*{Results and Discussion}
+\subsection*{Results}
+We will use the best model from hyperparameter tuning to make predictions on the testing set and generate our final result.
+Our model has never seen the test set before, so this performance should be a good indicator of how the model would perform if deployed in the real world.
 
-\section*{Results and Discussion}
-The results section details your metrics and experiments for the assessment of your solution. It allows you to compare your idea with other approaches you've tested.
+\begin{figure}[!htb]
+	\centering
+    \includegraphics[scale=0.45]{linear.png}
+    \caption{Results of linear regression for overall rating prediction.}\label{fig3}
+\end{figure}
+
+\begin{figure}[!htb]
+	\centering
+    \includegraphics[scale=0.45]{nn.png}
+    \caption{Results of neutral network for overall rating prediction.}\label{fig4}
+\end{figure}
+
+Figures \ref{fig3} and \ref{fig4} shows the results of linear regression and neural network on our testing set.
+
+On Predictions-Overall Rating axis, the testing results are close to $y=x$, which indicates that our prediction results are almost the same as actual values.
+This shows that our model performs well in predicting the ability of a player given his / her metrics.
+
+Besides, for our linear regression model, we also plot its coefficients for all 4 position categories.
+Figure \ref{fig5} shows the coefficients of linear regression model for players of each position categories.
+
+\begin{figure}[!htb]
+	\centering
+    \includegraphics[scale=0.5]{coefs.png}
+    \caption{Coefficients of linear regression model.}\label{fig5}
+\end{figure}
 

### 2021-12-12 Paper/main.tex
Final version of main.tex

@@
 
-    To demonstrate the benefits of our model, we built various charts and evaluated it. In our experiments, neural networks could ... compared to liner regression.
+    To demonstrate the benefits of our model, we built various charts and evaluated it.
+In our experiments, we evaluate the performance of 5 different models, which are Linear Regression, Random Forest, Gradient Boosted, K-Nearest Neighbors and Neural Network.
+Finally, we choose the best model and the most useful model among all these models and discussed their different usages.
 
@@
 \section*{Results and Discussion}
-\subsection*{Results}
 We will use the best model from hyperparameter tuning to make predictions on the testing set and generate our final result.
@@
 
+Invesgating these parameters, we have some interesting observations. The value of parameters can reflect the significance of an ability to a position. Below we take midfielders as an example.
+
+We use Python's $heapq$ library to find the 5 largest coefficients and their corresponding attribute names of linear regression model for midfielders. The results are shown in the table below.
+
+\begin{table}[htpb]
+    \centering
+    \begin{tabular}{|l|l|}
+    \hline
+    \textit{Attribute Name}             &       \textit{Coefficient Value} \\ \hline
+    \textit{BallControl}                &       \textit{0.24730435} \\ \hline
+    \textit{ShortPassing}               &       \textit{0.18084552} \\ \hline
+    \textit{Reactions}                  &       \textit{0.14724705} \\ \hline
+    \textit{Dribbling}                  &       \textit{0.07184282} \\ \hline
+    \textit{Age}                        &       \textit{0.06818059} \\ \hline
+    \end{tabular}
+    \caption{The 5 largest coefficients and their corresponding attribute names.}
+\end{table}
+
+From this table, we can observe that the main attributes contributing to a midfielder's overall rating are ball control, short passing, reactions and dribbling.
+This actually matches the reality, since normally a midfielder should control the ball and try to pass it to attacking players nearby.
+Besides, an older midfielder tends to have higher overall rating.
+This also shows that a midfielder with more experience is highly appreciated, since $Age$ also has a high coefficient value.
+
+The attributes with high coefficients highly reflects the requirement of corresponding position.
+In this way, these information can be quite useful for soccer clubs to design suitable tactics or to improve their training for their own players.
+A soccer team can even use its own player data to train these coefficients, and inspect which attributes reflects the team's style, and then pay more attention to practicing on these aspects in their youth training.
+
+In summary, neural network model performs a little bit better on accurately predicting overall ratings, while linear regression can provide more information about positions to soccer clubs.
+From our perspective, these 2 models can be used cooperatively for soccer clubs.
+Neural network can give accurate prediction for ratings to find potent players, and linear regression can be used to provide information for helping cultivating young players or planning tactics.
+
 \nocite{*}

### 2021-12-12 Paper/main.tex
fix

--- 2021-12-11 Paper/main.tex
@@
 
-    Although the $overall$ rating is the most important value either in the real football market or FIFA games, the official rating criteria is still not published.
+    Although the $overall$ rating is the most important value either in the real football market or FIFA games, the official rating criteria are still not published.
 Our model is to predict the $overall$ rating of players given their several capability values.
-Specially, we will divide players' position into 4 categories: forwards / strikers, midfielders, backfielders and goalkeepers, and we will predict overall ratings for each of these categories respectively.
+Specially, we will divide players' positions into 4 categories: forwards/strikers, midfielders, backfielders, and goalkeepers, and we will predict overall ratings for each of these categories respectively.
 
-    To demonstrate the benefits of our model, we built various charts and evaluated it. In our experiments, neural networks could ... compared to liner regression.
+    To demonstrate the benefits of our model, we built various charts and evaluated them.
+In our experiments, we evaluate the performance of 5 different models, which are Linear Regression, Random Forest, Gradient Boosted, K-Nearest Neighbors, and Neural Network.
+Finally, we choose the best model and the most useful model among all these models and discussed their different usages.
 
@@
 Intuitively, the metrics of a player can affect the overall rating of a player.
-However, the exact rating criteria is still not published.
+However, the exact rating criteria are still not published.
 Data analysis on soccer players' performance and abilities are being more and more valued by current soccer clubs.
@@
 to choose the best one or give any persuasive insights or conclusions.
-Our project tries different models for rating prediction and determine their performances to find the best model and give insightful conclusions and opinions.
+Our project tries different models for rating prediction and determines their performances to find the best model and give insightful conclusions and opinions.
 
@@
 
-Our project dataset is FIFA 2019 players attributes dataset, which is collected from Kaggle.
+Our project dataset is FIFA 2019 players attribute dataset, which is collected from Kaggle.
 This dataset includes 89 attributes of a soccer player, and our project only uses some of these attributes concerning only player capability.
-Details of data processing will be deeply illustrated in Dataset chapter.
+Details of data processing will be deeply illustrated in the Dataset chapter.
 
-We will implement linear regression and neural network in our project.
-Solution chapter gives the details of our models, including their hyperparameters.
-In order to finish this model fitting and predicting process, we plan to randomly select data from our dataset, and then split the selected data into training and testing sets to implement cross validation.
+We will implement linear regression and neural networks in our project.
+The solution chapter gives the details of our models, including their hyperparameters.
+To finish this model fitting and predicting process, we plan to randomly select data from our dataset, and then split the selected data into training and testing sets to implement cross-validation.
 
@@
 Besides, we will inspect the difference between these 2 models in practical use, and will mainly evaluate the usefulness of parameters of linear regression.
-This part will be further discussed in Results and Discussion chapter.
+This part will be further discussed in the Results and Discussion chapter.
 
@@
 
-Our project dataset is FIFA 2019 players attributes dataset, which is collected
+Our project dataset is FIFA 2019 players attribute dataset, which is collected
 from Kaggle. This dataset includes 89 attributes of a soccer player, and our
 project only uses some of these attributes concerning only player capability.
-Besides, considering that goalkeepers have a totally different set of capability
+Besides, considering that goalkeepers have a different set of capability
 metrics compared with other players, we will only consider data records of nongoalkeepers in our model.
@@
 \par Our model only focuses on predicting the overall rating of a player.
-Thus, we only need to keep those attributes related to the ability of players and drop the other irrelavent attributes.
+Thus, we only need to keep those attributes related to the ability of players and drop the other irrelevant attributes.
 Besides, our model does not consider ratings on different positions for the same player.
@@
 In this way, we can get rid of this String-typed attribute.
-Besides, in real soccer industry, players can actually be categoried according to their positions.
+Besides, in the real soccer industry, players can be categorized according to their positions.
 We mainly divide players into 4 positions: \textbf{Forward}, \textbf{Midfielder}, \textbf{Back}, and \textbf{Goalkeeper}.
@@
 In which $Mean$ and $Variance$ are the mean and variance of the original data $Original$.
-After this normalization, we output all 4 categoried datasets and the original dataset into 5 CSV files respectively.
+After this normalization, we output all 4 categorized datasets and the original dataset into 5 CSV files respectively.
 
@@
 In feature selection, we remove features that do not help our model learn the relationship between features and the target.
-This can help the model generalize better to new data and results in a more interpretable model.
+This can help the model generalize better to new data and result in a more interpretable model.
 Generally, I think of feature selection as subtracting features so we are left with only those that are most important.
@@
     \item Delete missing values
-    \item Remove features features that do not have a significant effect on the dependent variable or prediction of output by backward elimination.
+    \item Remove features that do not have a significant effect on the dependent variable or prediction of output by backward elimination.
 \end{itemize}
@@
 To compare the models, we are going to be mostly using the Scikit-Learn defaults for the model hyperparameters.
-Generally these will perform decently, but should be optimized before actually using a model.
-At first, we just want to determine the baseline performance of each model, and then we can select the best performing model for further optimization using hyperparameter tuning.
+Generally, these will perform decently but should be optimized before actually using a model.
+At first, we just want to determine the baseline performance of each model, and then we can select the best-performing model for further optimization using hyperparameter tuning.
 The default hyperparameters will get a model up and running, but nearly always should be adjusted using some sort of search to find the best settings for your problem!
@@
 Root Mean Square Error (RMSE) is the standard deviation of the residuals (prediction errors).
-Residuals are a measure of how far from the regression line data points are; RMSE is a measure of how spread out these residuals are.
+Residuals are a measure of how far from the regression line data points are; RMSE is a measure of how to spread out these residuals are.
 In other words, it tells you how concentrated the data is around the line of best fit.
@@
 It represents the proportion of variance (of y) that has been explained by the independent variables in the model.
-It provides an indication of goodness of fit and therefore a measure of how well unseen samples are likely to be predicted by the model, through the proportion of explained variance.
+It provides an indication of goodness of fit and therefore a measure of how well unseen samples are likely to be predicted by the model, though the proportion of explained variance.
 
@@
 Figures \ref{fig1} and \ref{fig2} shows our results of running all 5 models mentioned above.
-Depending on the run (the exact results change slighty each time), the Neutral Network performs the best.
-We have to admit that this is not the most fair comparison because we are using mostly the default hyperparameters.
+Depending on the run (the exact results change slightly each time), the Neutral Network performs the best.
+We have to admit that this is not the fairest comparison because we are using mostly the default hyperparameters.
 Nonetheless, from these results, we can conclude that machine learning is applicable because all the models significantly outperform the baseline.
-From here, We are going to concentrate on optimizing the best model using hyperparamter tuning.
-Given the results here, Neutral Network has the best performance of all these 5 models.
-However, consider that only linear regression can give coefficients for each attributes among all these models, linear regression can generate more information and has higher usability than other models.
-Thus, we will focus on both linear regression and neural network in the following part.
+From here, We are going to concentrate on optimizing the best model using hyperparameter tuning.
+Given the results here, Neural Network has the best performance of all these 5 models.
+However, considering that only linear regression can give coefficients for each attribute among all these models, linear regression can generate more information and has higher usability than other models.
+Thus, we will focus on both linear regression and neural networks in the following part.
 
@@
 Model hyperparameters are best thought of as settings for a machine learning algorithm that are tuned by the data scientist before training.
-Examples would be the number of trees in the random forest, or the number of neighbors used in K Nearest Neighbors Regression.
+Examples would be the number of trees in the random forest or the number of neighbors used in K Nearest Neighbors Regression.
 
@@
 We as data scientists control a model by choosing the hyperparameters, and these choices can have a significant effect on the final performance of the model (although usually not as great of an effect as getting more data or engineering features).
-Tuning the model hyperparameters controls the balance of under vs over fitting in a model.
+Tuning the model hyperparameters controls the balance of under vs overfitting in a model.
 We can try to correct for under-fitting by making a more complex model, such as using more trees in a random forest or more layers in a deep neural network.
-A model that underfits has high bias, and occurs when our model does not have enough capacity (degrees of freedom) to learn the relationship between the features and the target.
+A model that underfits has high bias and occurs when our model does not have enough capacity (degrees of freedom) to learn the relationship between the features and the target.
 We can try to correct for overfitting by limiting the complexity of the model and applying regularization.
-This might mean decreasing the degree of a polynomial regression, or adding dropout layers to a deep neural network.
+This might mean decreasing the degree of polynomial regression or adding dropout layers to a deep neural network.
 A model that overfits has high variance and in effect has memorized the training set.
@@
 
-Figures \ref{fig3} and \ref{fig4} shows the results of linear regression and neural network on our testing set.
+Figures \ref{fig3} and \ref{fig4} show the results of linear regression and neural network on our testing set.
 
-On Predictions-Overall Rating axis, the testing results are close to $y=x$, which indicates that our prediction results are almost the same as actual values.
+On the Predictions-Overall Rating axis, the testing results are close to $y=x$, which indicates that our prediction results are almost the same as actual values.
 This shows that our model performs well in predicting the ability of a player given his / her metrics.
@@
 Besides, for our linear regression model, we also plot its coefficients for all 4 position categories.
-Figure \ref{fig5} shows the coefficients of linear regression model for players of each position categories.
+Figure \ref{fig5} shows the coefficients of the linear regression model for players of each position category.
 
@@
 
+Investigating these parameters, we have some interesting observations. The value of parameters can reflect the significance of the ability to a position. Below we take midfielders as an example.
+
+We use Python's $heapq$ library to find the 5 largest coefficients and their corresponding attribute names of the linear regression model for midfielders. The results are shown in the table below.
+
+\begin{table}[htpb]
+    \centering
+    \begin{tabular}{|l|l|}
+    \hline
+    \textit{Attribute Name}             &       \textit{Coefficient Value} \\ \hline
+    \textit{BallControl}                &       \textit{0.24730435} \\ \hline
+    \textit{ShortPassing}               &       \textit{0.18084552} \\ \hline
+    \textit{Reactions}                  &       \textit{0.14724705} \\ \hline
+    \textit{Dribbling}                  &       \textit{0.07184282} \\ \hline
+    \textit{Age}                        &       \textit{0.06818059} \\ \hline
+    \end{tabular}
+    \caption{The 5 largest coefficients and their corresponding attribute names.}
+\end{table}
+
+From this table, we can observe that the main attributes contributing to a midfielder's overall rating are ball control, short passing, reactions, and dribbling.
+This matches the reality since normally a midfielder should control the ball and try to pass it to attacking players nearby.
+Besides, an older midfielder tends to have a higher overall rating.
+This also shows that a midfielder with more experience is highly appreciated since $Age$ also has a high coefficient value.
+
+The attributes with high coefficients highly reflect the requirement of the corresponding position.
+In this way, this information can be quite useful for soccer clubs to design suitable tactics or to improve their training for their own players.
+A soccer team can even use its own player data to train these coefficients and inspect which attributes reflect the team's style, and then pay more attention to practicing on these aspects in their youth training.
+
+In summary, the neural network model performs a little bit better on accurately predicting overall ratings, while linear regression can provide more information about positions to soccer clubs.
+From our perspective, these 2 models can be used cooperatively for soccer clubs.
+The neural network can give an accurate prediction for ratings to find potent players, and linear regression can be used to provide information for helping cultivate young players or planning tactics.
+
 \nocite{*}
